
---
title: "Legal document processing"
author: "Xia YIwei, Nemo"
date: "Sunday, January 01, 2017"
output: html_document
---

#Chinese legal documents processing

In the year 2014, the Chinese supreme people's court has release a **[document](http://www.chinacourt.org/article/detail/2013/11/id/1152212.shtml)** to collect and publish all the sentence documents made by court at each level in China.  

Some useful tools are needed to analyzing those Chinese document. Hence the aim of current R package  

Current R package relies on [Rwordseg](https://github.com/lijian13/Rwordseg) package made by Lijian



##1.Websites of legal documents
* [Offical website](http://wenshu.court.gov.cn/)
* [OpenLaw](http://openlaw.cn/)

##2.Aims 
* Develop useful R functions to do the Chinese word process 
* Package those functions into Github
* For general Chinese word processing  

##3.Developed functions
## 5.install all the functions
```{r eval=TRUE}

install_r<-function(site,pkg){
  #source R function
  source_https <- function(url, ...) {
  # load package
  require(RCurl)
 
  # parse and evaluate each .R script
  sapply(c(url, ...), function(u) {
    eval(parse(text = getURL(u, followlocation = TRUE, cainfo = system.file("CurlSSL", "cacert.pem", package = "RCurl"))), envir = .GlobalEnv)
  })
}
  
  #read all the function
  for(i in 1:length(pkg)) {
  source_https(paste0(site,pkg))  
  }
}


install_r("https://raw.githubusercontent.com/xxxw567/R-Chinese-Word-Processing/master/R/",c("chinntoda.R","cnextract.R","basic_cn.R"))

```




* basic funcs (input输入字符串, find目标字符串)
1. ischinexist  
2. findpos  
3. cutsentence  



*  cnextract  
Extract from A to B,  position A+1 to b  

```{r }

cnextract("判处有期徒刑十二年,缓刑一年","判处",",")


```

* Chinese words to date/number  
Single chinese character to number or to number of month 支持小于100年,单个中文字符,如果非中文,返回原始值

```{r }

chinntoda("五")
chinntoda("一年")
chinntoda("one")

```

* Convert Chinese number to Arabic Number
> 这个有点难,其实交给其他软件做更好

```{r}


a<-"181208900.00"
b<-"三十万"
c<-"45万"
d<-"5.9万"
e<-"三千余"
f<-"6万余"
g<-"3百万"
h<-"310万"
i<-"300000余"
j<-"3.98万"
k<-"九万"
l<-"壹佰万"
m<-"三十三万"
n<-"三百三十三万"
o<-"三千三百三十三万"
p<-"三千三百三十三万四千五百二十九"
r<-"万叁仟"

sapply(c(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p),codemoney)

```


## 4.Useful links

[how to write R package](http://cos.name/2011/05/write-r-packages-like-a-ninja/)  
[how source file in GitHub](https://tonybreyal.wordpress.com/2011/11/24/source_https-sourcing-an-r-script-from-github/)




