
#Chinese legal documents processing

In the year 2014, the Chinese supreme people's court has release a **[document](http://www.chinacourt.org/article/detail/2013/11/id/1152212.shtml)** to collect and publish all the sentence documents made by court at each level in China.  

Some useful tools are needed to analyzing those Chinese document. Hence the aim of current R package  

Current R package relies on [Rwordseg](https://github.com/lijian13/Rwordseg) package made by Lijian



##1.Websites of legal documents
* [Offical website](http://wenshu.court.gov.cn/)
* [OpenLaw](http://openlaw.cn/)

##2.Aim 
* Develop useful R functions to do the Chinese word process 
* Package those functions into Github
* For general Chinese word processing  

```{r include = FALSE}

```


##3.Developed functions
* Some Basic functions
  Check exist
*  cnextract  
Extract from A to B,  position A+1 to b  
```{r }
  include = FALSE
  cnextract("判处有期徒刑五年,缓刑两个月","判处",",")

```
* Chinese words to date/number
* Convert Chinese number to Arabic Number
