
---
title: "Legal document processing"
author: "Xia YIwei, Nemo"
date: "Sunday, January 01, 2017"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Chinese legal documents processing

In the year 2014, the Chinese supreme people's court has release a **[document](http://www.chinacourt.org/article/detail/2013/11/id/1152212.shtml)** to collect and publish all the sentence documents made by court at each level in China.  

The goal of current R package(functions) is tried to develop some useful tools to analyzing those Chinese document.   

Current R package depends on [Rwordseg](https://github.com/lijian13/Rwordseg) package made by Lijian, please install the package before make full use of the current package. 



##1.Websites of legal documents
* [Offical website](http://wenshu.court.gov.cn/)
* [OpenLaw](http://openlaw.cn/)

##2.Aims 
* Develop a useful R package process the Chinese characters in Legal documents
* Other types of Chinese documents


## 3.Install this package
```{r eval=TRUE, message = FALSE,warning = FALSE}
library(devtools)
install_github("xxxw567/legalwordproc")
library(legalwordproc)
```



##4.Developed functions

See the ?functions for more details

* chinntoda	  
Translate a single Chinse Date or Chinese number into Arabic number  
* cnextract	  
Cut a chinese sentence based on a given start and end  
* codemoney	  
Translate Chinese number into Arabic number
* cutsentence	  
Cut the Chinese sentences by given characters  
* findpos	  
Find the position of a certain Chinese word.
* is.num_coma	  
Detech whether a given chinese word is numeric or "."   * ischinexist  	 
Check whether a certain word is exist.  

### Some examples
* Cut a chinese sentence based on a given start and end 
```{r eval=TRUE, message = FALSE,warning = FALSE}

cnextract("判处有期徒刑十二年,缓刑一年","判处",",")


```

* Chinese words to date/number  

```{r eval=TRUE, message = FALSE,warning = FALSE}

chinntoda("五")
chinntoda("一年")
chinntoda("one")

```

* Convert Chinese number to Arabic Number  
>  这个有点难,其实交给其他软件做更好

```{r eval=TRUE, message = FALSE,warning = FALSE}


a<-"181208900.00"
b<-"三十万"
c<-"45万"
d<-"5.9万"
e<-"三千余"
f<-"6万余"
g<-"3百万"
h<-"310万"
i<-"300000余"
j<-"3.98万"
k<-"九万"
l<-"壹佰万"
m<-"三十三万"
n<-"三百三十三万"
o<-"三千三百三十三万"
p<-"三千三百三十三万四千五百二十九"

matrix(sapply(c(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p),codemoney))

```

* Cut the Chinese sentences by given characters  
```{r eval=TRUE, message = FALSE,warning = FALSE}

cutsentence ("本院认为，被告人王兴玖、梅潋耀身为安全管理人员，在生产作业中违反安全管理规定，不认真履行职责、发生重大安全事故，致一人死亡，其行为均已构成重大责任事故罪。公诉机关指控的事实、罪名成立，予以确认。",c("，","。"))


```

## 5.Useful links


* [how to source file in GitHub](https://tonybreyal.wordpress.com/2011/11/24/source_https-sourcing-an-r-script-from-github/)  
* [how to download data from GitHub](https://github.com/opetchey/RREEBES/wiki/Reading-data-and-code-from-an-online-github-repository)  
* [inroduction of Rmarkdown](http://rmarkdown.rstudio.com/?version=0.98.1103&mode=desktop)  
* [Rmarkdown chectsheet](http://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf)  
* [RStudio+Markdown+Pandoc](http://www.jianshu.com/p/a97b4a9f6d5b)  

* [how to write R package](http://cos.name/2011/05/write-r-packages-like-a-ninja/)  
* [write R package1_2013](http://blog.fens.me/r-package-faster/)  
* [write R package2_2013](http://blog.fens.me/r-build-package/)  
